Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more

We presented a translation scheme that makes more SMT problems amenable to
finite model findings in SMT. In conjunction with the finite model finding
techniques introduced by Reynolds et al.\
\cite{ReyEtAl-1-RR-13,reynolds-et-al-2013}, it makes it possible to
find models of quantified formulas over infinite types, such as integers
and algebraic datatypes.

In future work, it would be interesting to evaluate the approach against other
counterexample generators, notably Leon and Nitpick, and enrich the benchmark
suite with problems exercising \cvc's support for coalgebraic datatypes
\cite{reynolds-blanchette-2015-codata}. We also plan to integrate \cvc as a
counterexample generator in proof assistants. Finally, future work could also
include identifying further sufficient conditions for admissibility, thereby
enlarging the scope of the scheme presented here.

>>>>

We presented a translation scheme that makes more SMT problems amenable to
finite model findings in SMT. In conjunction with finite model finding
techniques,
%introduced by Reynolds et al.\ \cite{ReyEtAl-1-RR-13,reynolds-et-al-2013},
%%% Great work, but let's not cite it more than 4 times if it can be avoided. --jb
it makes it possible to
find models of quantified formulas over infinite types, such as integers
and algebraic datatypes.

In future work, it would be interesting to evaluate the approach against other
counterexample generators, notably Leon and Nitpick, and enrich the benchmark
suite with problems exercising \cvc's support for coalgebraic datatypes
\cite{reynolds-blanchette-2015-codata}. We also plan to integrate \cvc as a
counterexample generator in proof assistants. Finally, future work could also
include identifying further sufficient conditions for admissibility, thereby
enlarging the applicability of the translation scheme presented here.
